Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

The \dslSys{} captures the concepts of
\emph{device type}, \emph{component}, \emph{capability}, and \emph{requirement}.
%
A reference sample is presented in \Cref{lst:system-configuration}.
%
The DSL provides simple means to define capabilities as types in the host language (Lines~\ref{capab:start}--\ref{capab:end}),
and then to associate them to pulverised components for each device type (Lines~\ref{devcap:start}--\ref{devcap:end}).
%
This \ac{dsl} is meant to define constraints that the application imposes on the infrastructure,
ruling out configurations that are not capable to support the system
(for instance, deploying the sensor component of a device in a host that exposes no sensor).
%
All combinations of components and capabilities that are defined as supported become instead amenable as \emph{targets} of deployment or reconfiguration---forming what we may call the \emph{deployment range}.
%\emph{runtime reconfiguration}.
%
In the example, e.g., component \texttt{Behavior} in \texttt{iot-sensor} is defined as executable on any of host exposing
\texttt{HighCPU} and/or \texttt{EmbeddedDevice} as capabilities (\Cref{devcap:b}):
it implies that the component can be dynamically moved to any host offering any such capability.

>>>>

The \dslSys{} captures the concepts of
\emph{device type}, \emph{component}, \emph{capability}, and \emph{requirement}.
%
A reference sample is presented in \Cref{lst:system-configuration}.
%
The DSL provides simple means to define capabilities as types in the host language (Lines~\ref{capab:start}--\ref{capab:end})
and associate them with pulverised components for each device type (Lines~\ref{devcap:start}--\ref{devcap:end}).
%
This \ac{dsl} is meant to define constraints that the application imposes on the infrastructure,
ruling out configurations that are not capable to support the system
(for instance, deploying the sensor component of a device in a host that exposes no sensor).
%
All combinations of components and capabilities that are defined as supported become instead amenable as \emph{targets} of deployment or reconfiguration---forming what we may call the \emph{deployment range}.
%\emph{runtime reconfiguration}.
%
In the example, e.g., component \texttt{Behavior} in \texttt{iot-sensor} is defined as executable on any of host exposing
\texttt{HighCPU} and/or \texttt{EmbeddedDevice} as capabilities (\Cref{devcap:b}):
it implies that the component can be dynamically moved to any host offering any such capability.
